TBA

### 2020-07-14 manuscript.tex
First pull
more detailed outline

\section{\label{sec:intro}Introduction}

DNA motivation
\begin{enumerate}
	\item Connection to Tokmakoff results
	\item Some origami, sensor, other nanotech appications
\end{enumerate}

SRV motivation
\begin{enumerate}
	\item First time studying a two body problem
	\item Compare with other TICA-MSM approaches to DNA
	\item Compare with Noe nucleotide paper
\end{enumerate}

@@

Simulation set up

Featurization
\begin{enumerate}
	\item Vamp-2 score for permutable distances is slightly lower but should not contain degenerate information (SI data)
	\item Inverse distances have higher vamp-2 score than regular distances (SI data)
\end{enumerate}

SRV validation
\begin{enumerate}
	\item Plot loss scores and self-consistency check for each sequence (fig 1 and 2)
	\item Select number of slow modes (different for each) and lag time (same for each) based on this analysis.
	\item Only use off diagonals and add sequence visuals along axes (fig 3)
\end{enumerate}

MSM construction
\begin{enumerate}
	\item hyperparameters include: number of microstates, lag (use same as SRV), number of macrostates (usually n+1) but we use n states for GC-core and GC-mid. I have not done a full optimization sweep over these parameters, but can explain the motivation for choosing these.
    \item Can show comparison data with TICA -- timescales converge faster and state assignments tend to be more concrete (although this has varied) (fig 4)
\end{enumerate}

\section{\label{sec:methods}Discussion}

Brief description and diagrams for collective variables:
\begin{enumerate}
	\item Inverse average shifting distance
	\item Fourth basepair distances
\end{enumerate}

AT-all
\begin{enumerate}
	\item Dynamics dominated by slow shifting modes
	\item sources to verify this would be the case
	\item Minimal data from Tokmakoff on this, but can look at relative hybridization rates
	\item SI Calculations to prove preferred thermo stability of 5’ shifted state
\end{enumerate}

GC-end
\begin{enumerate}
	\item Similar dynamics to AT-all, but with overall lower stability and timescales
	\item Difficult to make any claims because the thermodynamics of external mismatches with dangling ends have not been measured experimentally, and 3spn2 does not paramertize these mismatches explicitly
	\item According to SantaLucia external mismatches and dangling ends tend to have weakly stabilizing effect, and there are 4-6 intact basepairs for these conformations
	\item Might account for unknown signal in 2018 Tokmakoff paper with timescale between the fraying and dehybrization signal, but not sure... 
\end{enumerate}

GC-core
\begin{enumerate}
	\item Frayed states requires the fourth base pair to be broken, most partially frayed states are not included in metastable clustering
	\item 2nd slow mode correlates well with expected fraying behavior, can sample along this mode and generally find increasing frayed states (although the SRV coords are spiky)
	\item 3rd mode is reflective of changes in orientation in dissociated behavior. This could be interesting for the SI, but this state does not inform the macrostate clustering
\end{enumerate}  
GC-mid
\begin{enumerate}
	\item Evidence of fraying correlations in higher order modes, but these are not consistent and their inclusion does not generate a metastable third mode
	\item Treat this as a two-states model, where fraying is an expected feature of the hybridized state but not does not characterize a metastable state
\end{enumerate}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/skeleton/AT-all_validation.PNG}
        \caption{For Supplemental info: Selection process for AT-all slow modes}
        \label{fig:AT-all_val}
	\end{center}
\end{figure}

@@

\bibliography{references}

>>>>

\section{\label{sec:intro}Introduction}
Should be 4-5 paragraphs with similar structure to other papers in the field.
-Funnel shaped to highlight general DNA technologies (oligomers and

\subsection{\label{sec:intro}DNA motivation}
\subsubsection{\label{sec:intro}Main Question: how does sequence determine the kinetics of DNA oligonucleotides}

\subsubsection{\label{sec:intro}What is known about the system and what remains an open question -- reference Tokmakoff frayed states here}

\subsubsection{\label{sec:intro}Thermodynamics are well established and some MSM based (high resolution kinetic) models have been employed to study kinetics}

\subsubsection{\label{sec:intro}Circle back to applications after discussing the open question that we are seeking to solve -- how does this expand on existing technolgies}

\subsection{\label{sec:intro}SRV motivation}
\subsubsection{\label{sec:intro}First time studying a two body problem}
\subsubsection{\label{sec:intro}Compare with other TICA-MSM approaches to DNA}

@@

-don't confuse methods plots with results
-not necessary to plot vamp-2 scores (or can include comaprisons in the SI)
-follow basic outline of Trp-Cage methods in the order sim, srv, msm (a lot of the msm will be in results, but can go through basic assumptions and pytemma pipeline)

\subsection{\label{sec:methods}Simulation set up}
\subsubsection{\label{sec:methods}Tmelt selection etc}

@@

\subsection{\label{sec:methods}SRV}
\subsubsection{\label{sec:methods}Featurization}
\begin{enumerate}
	\item Vamp-2 score for permutable distances is slightly lower but should not contain degenerate information (SI data)
	\item Inverse distances have higher vamp-2 score than regular distances (SI data)
\end{enumerate}

\subsubsection{\label{sec:methods}Select number of slow modes (different for each) and lag time (same for each) based on this analysis}

\subsection{\label{methods}MSM construction}
\begin{enumerate}
	\item hyperparameters include: number of microstates, lag (use same as SRV), number of macrostates (usually n+1) but we use n states for GC-core and GC-mid. I have not done a full optimization sweep over these parameters, but can explain the motivation for choosing these.
    \item Can show comparison data with TICA -- timescales converge faster and state assignments tend to be more concrete (although this has varied) (fig 4)
\end{enumerate}

\section{\label{sec:Results}Results}
- lead with same kind of diagram for each sequence, add additional figures when necessary for a given sequence

\subsection{\label{sec:Results}AT-all}
\subsubsection{\label{sec:Results}Explanation of state selection and slow modes}
\subsubsection{\label{sec:Results}Brief description and diagrams for collective variables}
\begin{enumerate}
	\item Inverse average shifting distance
	\item Fourth basepair distances
\end{enumerate}

\subsubsection{\label{sec:Results}Observations and key takeaways}
\begin{enumerate}
	\item Dynamics dominated by slow shifting modes
	\item sources to verify this would be the case
	\item Minimal data from Tokmakoff on this, but can look at relative hybridization rates
	\item SI Calculations to prove preferred thermo stability of 5’ shifted state
\end{enumerate}

\subsection{\label{sec:Results}GC-end}
\begin{enumerate}
	\item Similar dynamics to AT-all, but with overall lower stability and timescales
	\item Difficult to make any claims because the thermodynamics of external mismatches with dangling ends have not been measured experimentally, and 3spn2 does not paramertize these mismatches explicitly
	\item According to SantaLucia external mismatches and dangling ends tend to have weakly stabilizing effect, and there are 4-6 intact basepairs for these conformations
	\item Might account for unknown signal in 2018 Tokmakoff paper with timescale between the fraying and dehybrization signal, but not sure... 
\end{enumerate}

\subsection{\label{sec:Results}GC-core}
\begin{enumerate}
	\item Frayed states requires the fourth base pair to be broken, most partially frayed states are not included in metastable clustering
	\item 2nd slow mode correlates well with expected fraying behavior, can sample along this mode and generally find increasing frayed states (although the SRV coords are spiky)
	\item 3rd mode is reflective of changes in orientation in dissociated behavior. This could be interesting for the SI, but this state does not inform the macrostate clustering
\end{enumerate}

\subsection{\label{sec:Results}GC-mid}
\begin{enumerate}
	\item Evidence of fraying correlations in higher order modes, but these are not consistent and their inclusion does not generate a metastable third mode
	\item Treat this as a two-states model, where fraying is an expected feature of the hybridized state but not does not characterize a metastable state
\end{enumerate}

\subsection{\label{sec:Results}Compare all results together}
\subsubsection{\label{sec:Results}Figure showing Pearson correlations between leading modes on common basis}

\subsubsection{\label{sec:Results}Figure showing all sequences plotted on a common low dimensional space (probably the 2nd TICA mode and the 2nd GC-core mode)}

\begin{enumerate}
	\item Evidence of fraying correlations in higher order modes, but these are not consistent and their inclusion does not generate a metastable third mode
	\item Treat this as a two-states model, where fraying is an expected feature of the hybridized state but not does not characterize a metastable state
\end{enumerate}

\section{\label{sec:conc}Conclusion}
\subsection{\label{sec:Results}Looks a lot like the abstract}

\section{\label{sec:SI}Potential SI figures}
\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/skeleton/AT-all_validation.PNG}
        \caption{For Supplemental info: Selection process for AT-all slow modes}
        \label{fig:AT-all_val}
	\end{center}
\end{figure}

@@

%\bibliography{references}
Test cite: \citep{Zhang2018DeepMechanics}
\bibliography{refs_mendeley}
